Moral Foundations of U.S. Political News Organizations

### 2019-04-13 pilot_manuscript.Rmd
so rude

```{r exp1_source_descriptives, results = 'asis', echo = FALSE, message = F}

@@

```{r exp2_source_descriptives_kav, results = 'asis', echo = FALSE, message = F}
#Kav
final_kav$uniquewords = NA
final_kav$valenceavg = NA

@@

```{r exp2_source_descriptives_gs, results = 'asis', echo = FALSE, message = F}
#Kav
#GS
final_gs$uniquewords = NA
final_gs$valenceavg = NA

@@

```{r exp2-table_kav, results = 'asis', echo = F}
#MFD, mean, sd, mean, sd, t, p, d
tableprint_kav = matrix(NA, ncol = 8, nrow = 5)
colnames(tableprint_kav) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")

@@

```{r exp2-table_gs, results = 'asis', echo = F}
#MFD, mean, sd, mean, sd, t, p, d
tableprint_gs = matrix(NA, ncol = 8, nrow = 5)
colnames(tableprint_gs) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")

>>>>

```{r exp1sourcedescriptives, results = 'asis', echo = FALSE, message = F}

@@

```{r exp2sourcedescriptiveskav, results = 'asis', echo = FALSE, message = F}
#Kav
final_kav$uniquewords = NA
final_kav$valenceavg = NA

@@

```{r exp2sourcedescriptivesgs, results = 'asis', echo = FALSE, message = F}
#Kav
#GS
final_gs$uniquewords = NA
final_gs$valenceavg = NA

@@

```{r exp2-tablekav, results = 'asis', echo = F}
#MFD, mean, sd, mean, sd, t, p, d
tableprint_kav = matrix(NA, ncol = 8, nrow = 5)
colnames(tableprint_kav) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")

@@

```{r exp2-tablegs, results = 'asis', echo = F}
#MFD, mean, sd, mean, sd, t, p, d
tableprint_gs = matrix(NA, ncol = 8, nrow = 5)
colnames(tableprint_gs) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")
